### 2020-07-01 evaluation.tex
fig

\begin{figure}
 \centering
    \includegraphics[width=0.5\textwidth]{./pic/table1.pdf}
    \caption{Performance in Controlled Environment(Traditional Lenses)}
    \label{fig-control}
\end{figure}

\begin{figure}
 \centering
    \includegraphics[width=0.5\textwidth]{./pic/distance.pdf}
    \caption{Performance in Controlled Environment(Optical Zoom Lenses)}
    \label{fig-control2}
\end{figure}
\subsection{Performance In Random Environment}
We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Figure~\ref{fig-random} and Figure~\ref{fig-random2}). The model achieves an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses.

\begin{figure}
 \centering
    \includegraphics[width=0.5\textwidth]{./pic/table2.pdf}
    \caption{Performance in Random Environment(Traditional Lenses)}
    \label{fig-random}
\end{figure}

\begin{figure}
 \centering
    \includegraphics[width=0.5\textwidth]{./pic/distance2.pdf}
    \caption{Performance in Random Environment(Optical Zoom Lenses)}
    \label{fig-random2}
\end{figure}
We compare the results to discover the influence of the surrounding environment: The model performs best in daytime and weaker illumination may decrease its ability. Also, the model performs better at closer distances. As the model is trained initially on the 5m group data, it performs expecially well at this distance, while the accuracy at other distances experience certain levels of decrease. Also, similar to the experiments at controlled environments, random artifacts start to encompass OCR compensation, rendering the result images highly unreadable, until at 7.5m distance only the simplist characters can escape from being flooded by noize.

\subsection{Adapting Ability}
We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments. The results are shown in Figure~\ref{table-adapt}.Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.

\begin{figure}
 \centering
    \includegraphics[width=0.5\textwidth]{./pic/table3.pdf}
    \caption{Adapting Ability(Traditional Lenses)}
    \label{table-adapt}
\end{figure}

@@

\begin{figure}
 \centering
    \includegraphics[width=0.5\textwidth]{./pic/table4.pdf}
    \caption{Comparison with other architectures}
    \label{table-comp}
\end{figure}

% \section{System Evaluation}
\subsection{Accuracy}
We build the system on smartphone and evaluate its performance in real-life environments. We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim. As the telephoto cameras can assist the attacker to see clearly at approximately 3m distance without any aid from SR algorithms, we believe it's insignificant to further extend this distance to judge it as a threat to privacy, so that the following experiments are performed with traditional lenses at 1~2m range. We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model. No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty. The results are shown in Figure~\ref{table-accuracy}.

\begin{figure}
 \centering
    \includegraphics[width=0.5\textwidth]{./pic/table5.pdf}
    \caption{Accuracy in different real-life scenarios}
	\label{table-accuracy}
\end{figure}

@@

\begin{figure}
 \centering
    \includegraphics[width=0.5\textwidth]{./pic/table5.pdf}
\caption{Influence of hand tremors}
\label{table-tremor}
\end{figure}

@@

\begin{table}[] 
\centering
\begin{tabular}{@{}ccccc@{}}
	\toprule
Accuracy & Read text & Type text & Enter PIN & Enter password\\ \midrule
raw image & 5 & 0 & 0 & 0\\ \\
SRPeek & 100 & 100 & 100 & 80\\ \bottomrule
\end{tabular}

\caption{Success rate in different tasks.}
\label{table-task}
\end{table}

>>>>

\begin{figure*}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control}}
    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control2}}
    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random}}
    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
    \hfill
    \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
    \label{fig-performance-1}
\end{figure*}

% \begin{figure}
%  \centering
%     \includegraphics[width=0.5\textwidth]{./pic/table1.pdf}
%     \caption{Performance in Controlled Environment(Traditional Lenses)}
%     \label{fig-control}
% \end{figure}

% \begin{figure}
%  \centering
%     \includegraphics[width=0.5\textwidth]{./pic/distance.pdf}
%     \caption{Performance in Controlled Environment(Optical Zoom Lenses)}
%     \label{fig-control2}
% \end{figure}
\subsection{Performance In Random Environment}
We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Figure~\ref{fig-random} and Figure~\ref{fig-random-2}). The model achieves an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses.

% \begin{figure}
%  \centering
%     \includegraphics[width=0.5\textwidth]{./pic/table2.pdf}
%     \caption{Performance in Random Environment(Traditional Lenses)}
%     \label{fig-random}
% \end{figure}

% \begin{figure}
%  \centering
%     \includegraphics[width=0.5\textwidth]{./pic/distance2.pdf}
%     \caption{Performance in Random Environment(Optical Zoom Lenses)}
%     \label{fig-random-2}
% \end{figure}
We compare the results to discover the influence of the surrounding environment: The model performs best in daytime and weaker illumination may decrease its ability. Also, the model performs better at closer distances. As the model is trained initially on the 5m group data, it performs especially well at this distance, while the accuracy at other distances experience certain levels of decrease. Also, similar to the experiments at controlled environments, random artifacts start to encompass OCR compensation, rendering the result images highly unreadable, until at 7.5m distance only the simplest characters can escape from being flooded by noise.

\begin{figure*}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
    \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
    \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
    \hfill
    \caption{Performance for Adapting Ability and various processing images.}
    \label{fig:adapting}
\end{figure*}

\subsection{Adapting Ability}
We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments. The results are shown in Figure~\ref{fig-adapt-tranditional}.Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.

% \begin{figure}
%  \centering
%     \includegraphics[width=0.5\textwidth]{./pic/table3.pdf}
%     \caption{Adapting Ability(Traditional Lenses)}
%     \label{table-adapt}
% \end{figure}

@@

% \begin{figure}
%  \centering
%     \includegraphics[width=0.5\textwidth]{./pic/table4.pdf}
%     \caption{Comparison with other architectures}
%     \label{table-comp}
% \end{figure}

\begin{table}[!t]
    \centering
    \begin{tabular}{@{}cccc@{}}
        \toprule
    System & SRPeek & SRCNN & VideoSR \\ \midrule
    PSNR(db) & 13.32 & 7.69 & 8.403\\ 
    OCR Accuracy(\%) & 100 & 10 & 23\\ \bottomrule
    \end{tabular}
    \caption{Comparison with existing systems.}
    \label{table-comp}
\end{table}

% \section{System Evaluation}
\subsection{Accuracy}
We build the system on smartphone and evaluate its performance in real-life environments. We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim. As the telephoto cameras can assist the attacker to see clearly at approximately 3m distance without any aid from SR algorithms, we believe it's insignificant to further extend this distance to judge it as a threat to privacy, so that the following experiments are performed with traditional lenses at 1~2m range. We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model. No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty. The results are shown in Figure~\ref{table-scenarios}.

\begin{table}[!t]
    \centering
    \begin{tabular}{@{}cccc@{}}
        \toprule
    System & Home & Transport & Theater \\ \midrule
    Baseline & 5 & 0 & 0\\ 
    \midrule
    OCR & 100 & 10 & 23\\ 
    Human & 95 & 85 & 70\\ \bottomrule
    \end{tabular}
    \caption{Recognition accuracy in various scenarios.}
    \label{table-scenarios}
\end{table}

% \begin{figure}
%  \centering
%     \includegraphics[width=0.5\textwidth]{./pic/table5.pdf}
%     \caption{Accuracy in different real-life scenarios}
% 	\label{table-accuracy}
% \end{figure}

@@

\begin{table}[!t] 
    \centering
    \begin{tabular}{ccccc}
        \toprule
    System & None & Camera & Target & Both  \\
    \midrule
    Baseline & 5 & 0 & 5& 5\\ 
    \midrule
    OCR & 95 & 85 & 80 & 80\\ 
    Human & 95 & 85 & 80 & 85\\ \bottomrule
    \end{tabular}
    \caption{Impact of hand tremors while holding various items.}
    \label{table-tremor}
\end{table}

% \begin{figure}
%  \centering
%     \includegraphics[width=0.5\textwidth]{./pic/table5.pdf}
% \caption{Influence of hand tremors}
% \label{table-tremor}
% \end{figure}

@@

\begin{table}[!t]
\centering
\begin{tabular}{@{}ccccc@{}}
	\toprule
Accuracy & Read text & Type text & Enter PIN & Enter password\\ \midrule
Raw Image & 5 & 0 & 0 & 0\\
SRPeek & 100 & 100 & 100 & 80\\ \bottomrule
\end{tabular}
\caption{Success rate in different tasks.}
\label{table-task}
\end{table}
